### 2019-05-03 monograph/thesis/chapters/object_beautifier.tex
Revert "Correções para linux"
This reverts commit 7b06cc8c2bcfdd290cc6dda351b7de9524f5d1cb.
Moved the section related works to object_beautifier.tex
Moved the Introduction from object_beautifier.tex to theorybase.tex

\section{Introduction}

TODO:
Explains what does `translation` means and what is a translator,
compiler,
etc.
(the first slide contents' from Introdução a Compiladores)

This work aims to propose a translator,
where the input and output languages are the same language.
Such translation objective is to change the language representational structure,
but without affecting the language lex,
syntactic or semantics, i.e.,
the language meaning.

This program class is commonly know as text formatters.
The differential from this work from others is the goal of a single expandable tool,
capable of manipulating all existent and future programming languages,
based on the use of deterministic
% TODO:\cite{deterministic free grammars explanation}
and controlled nondeterministic
% \cite{TODO:section explaning what does controlled means}
context free grammars.

@@

// Defines a expression which will map the ending of a exclusion block.
Scope End:
\\\*
\end{lstlisting}

@@

>>>>

\section{Como implementar}

@@

// Defines a expression which will map the ending of a exclusion block.
Scope End:
\\\*
\end{lstlisting}
\vspace*{-4mm}

@@

\section{\lang{Related Works}{Trabalhos Relacionados}}

\url{http://editorconfig.org/}

### 2019-05-03 monograph/thesis/chapters/theorybase.tex
Moved the Introduction from object_beautifier.tex to theorybase.tex

>>>>

\section{Tradução de Código}

TODO:
Explains what does `translation` means and what is a translator,
compiler,
etc.
(the first slide contents' from Introdução a Compiladores)

This work aims to propose a translator,
where the input and output languages are the same language.
Such translation objective is to change the language representational structure,
but without affecting the language lex,
syntactic or semantics, i.e.,
the language meaning.

This program class is commonly know as text formatters.
The differential from this work from others is the goal of a single expandable tool,
capable of manipulating all existent and future programming languages,
based on the use of deterministic
% TODO:\cite{deterministic free grammars explanation}
and controlled nondeterministic
% \cite{TODO:section explaning what does controlled means}
context free grammars.
